Symbolic linearization of equations of motion of constrained multibody systems

### 2014-08-29 response_to_reviewers_aug_2014.txt

In summary, we have addressed as many of the comments as possible, but feel
that the other comments not addressable, and suggest that Reviewer #1 has
not made enough of an effort to either comprehend the paper, or communicate
where they had difficulty comprehending it. As Reviewer #2 seems to
approve of the manuscript, we would ask that you overlook Reviewer #1's
concerns when making the decision to publish or reject this work.

Thank you,
Dale Peterson
Gilbert Gede
Mont Hubbard

Response to Reviewer #1.

1. Abstract. "...but is compatible with any method as long as only ordinary
    differential equations are required to describe the system, and independent
    and dependent states remain in the final equations (i.e. no DAE's,
    dependent variables are not substituted away)". The sentence, and
    especially its end, is still not clear to me.

@@

Author Response: We have changed the sentence for clarity. It now more clearly
specifies the types of differential equations which can be used.  It also
clarifies that it was developed for use with Kane's Method when dependent
quantities have not been algebraically eliminated.

2. 1. 36-37 (page 1, lines 36-37). "Design of linear state feedback controllers
    and first order stability analysis of equilibria are two of the most common
    uses of multibody system dynamics models". I am not sure about these are
    the most common uses.

@@

Author Response: We removed the words which suggested that these were the most
common uses, instead stating that they are just common uses.

3. 2. 1-19. The paragraph is still unclear to me. Kane’s equations are the
   projections of the initial (expressed in dependent velocities and as such
   constraint reaction-induced) dynamic equations into the directions of
   generalized speeds, which are by assumption independent for a constrained
   system, and with these projections the constraint reactions are excluded
   from evidence. If the projected dynamic equations are still expressed in the
   dependent velocities (not in the generalized speeds), the number of the
   projected dynamic equations is smaller than the number of the velocities. In
   this context I do not understand the remark that "The kinematical and
   dynamical differential equations can be solved for the time derivatives of
   the generalized coordinates and generalized speeds, ..." as well as most of
   the content of the paragraph. My reservations raised in the previous review
   were not clarified.

@@

du/dt = f / m

We welcome specific suggestions about how this can be made more clear.

Section 2 was introduced specifically to clarify how we use Kane's method since
some of our notation deviates from his presentation in his 1985 book. When the
system has velocity constraints (i.e., a non-minimal set of generalized speeds
are introducted, or the system has time differentiated holonomic constraints),
the velocity constraint matrix B (equation 11 in the paper) can manipulated to
form matrix A (equation 21 in the paper). This A matrix is used to reduce the
number of equations for generalized speeds by the number of constrained speeds.
This is also outlined by Kane in [Kane 1985], in equations 4.4.3 and 4.4.11,
which shows the reduction in size of the equations for the generalized speeds
and that _all_ the speeds (dependent and independent) are still present.

4. 2. 20-27. I am not totally satisfied with the changes/clarifications made by
    the Authors. For example, the remark "Velocity constraints often appear
    where there is rolling without slip or there are closed kinematic loops" is
    unclear (if correct at all). Velocity constraints, or, better, constraint
    equations at the velocity level, are either nonholonomic constraints (often
    consequent to the rolling without slip) or differentiated with respect to
    time holonomic constraint equations (one source of such constraints are
    closed kinematic loops).

@@

Author Response: We have rewritten this entire paragraph to ensure that the
description of each level of constraints is consistent, and more clear. We have
reworked the sentence in question to more clearly state that things like
rolling without slip lead to nonholonomic constraints and closed kinematic
loops lead to time differentiated holonomic constraints, both of which are
velocity level constraints.

5. 5. 25-50. The velocity constraints are introduced in Eq. (8) in a general
    (nonlinear) form f_v (q,u,t) = 0 . It is then said that “By assumption (why
    "by assumption”?), the velocity constraints are linear with respect to u,
    ... which implies Bu + fvt(q,t) = 0". Firstly, in general, the constraint
    matrix B is not constant, i.e.  B(q) or even B(q,t). Then, why the velocity
    constraints were not introduced from the beginning in this "linear" form?

@@

Author Response: We have clarified that the B matrix is a function of the
coordinates and time, even though it is written as only a single symbol (a
format which we use throughout the paper).

6. 8. 15 and 831. The meaning of the “exogenous inputs” is not well
    motivated/explained.

Author Response: We believe that the sentence "The s exogenous inputs include
control system inputs and/or external disturbance forces or torques applied to
the system." explains that the exogenous inputs include forces/torques which
are not internal to the system (e.g. a reaction force), but instead applied
from outside the system (a motor driving a body in the system).

7. A general remark to Section 2. While Kane’s method is generally well
    understood, the Authors presentation of its formulation is rather
    "frustrating".

### 2014-09-29 PetersonGedeHubbard2012.tex
Remove extra '}' in math mode

\section{Introduction}
\label{sec:intro}
Design of linear state feedback controllers and first order stability analysis
are common uses of multibody system dynamics models. Both require linearized
equations of motion.  We define a constrained system to be one whose
configuration has been described by a non-minimal set of generalized
coordinates or whose motion has been described by a non-minimal set of
generalized speeds.  For unconstrained systems (with a minimal set of
generalized coordinates and speeds), obtaining the linearized equations of
motion is as simple as arranging them in first order form ($\dot{x} = f(x, t)$)
and evaluating $\frac{\partial f}{\partial x}}$ at the point of interest.
However, when the system has constraints not all the states (coordinates and
speeds) are independent, and this process is not as straightforward.

>>>>

\section{Introduction}
\label{sec:intro}
Design of linear state feedback controllers and first order stability analysis
are common uses of multibody system dynamics models. Both require linearized
equations of motion.  We define a constrained system to be one whose
configuration has been described by a non-minimal set of generalized
coordinates or whose motion has been described by a non-minimal set of
generalized speeds.  For unconstrained systems (with a minimal set of
generalized coordinates and speeds), obtaining the linearized equations of
motion is as simple as arranging them in first order form ($\dot{x} = f(x, t)$)
and evaluating $\frac{\partial f}{\partial x}$ at the point of interest.
However, when the system has constraints not all the states (coordinates and
speeds) are independent, and this process is not as straightforward.
